Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-04 ms.tex
small changes to global parameters table
complete overhaul of correlation slope global parameters section, overhaul of corresponding table as well

\subsubsection{Relative Zero Level}

@@

\begin{deluxetable}{rrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{6} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Model} &
\colhead{Data} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$}
}
\startdata
 1 & FIRAS+\verb|i100| & 0.0363 & 13.0 & 1.67 & 2.70 \\
 2 & \PLANCK+\verb|i100| & 0.0485 & 8.22 & 1.63 & 2.82 \\ [-2ex]
\enddata
\end{deluxetable}

@@

In light of the \PLANCK~HFI data, it is possible to revisit the best-fit global
parameters of the two-component emission model. To derive the 
\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
maps, we employed a correlation slope analysis (see Figure XX). Specifically,
we correlated the observed \PLANCK~data against the appropriate FDS99 
prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
consideration due to the sensitivity of the 100 GHz trend to our ad hoc
low order corrections (see Figure \ref{fig:harm}). All comparisons between
\PLANCK~and the FDS99 predictions were made after smoothing both to 
$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
excellent.

@@

However, the slopes at low frequencies are not precisely unity, as would
be expected if the global two-component parameters derived from FIRAS by
FDS99 were also the best-fitting global parameters with respect to the 
\PLANCK~data set.

@@

We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
the correlation slopes and their uncertainties given in Table QQ by 
taking $T_2$=$16.2$K and running Markov chains to sample the posterior:

Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
strong covariances, but even so several conclusions are clear: (1) a lower 
value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
is effectively identical to that found by FDS99 to within uncertainties and (3)
a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
strongly covariant with $\beta_1$, the difference of $f_1$ between the 
\PLANCK~and FIRAS best fits is not particularly significant.

@@

The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
separately for both model 1 (FIRAS+\verb|i100|) and model 2 
(\PLANCK+\verb|i100|), each defined by their respective global parameters 
listed in Table \ref{tab:global}.

>>>>

\subsubsection{Relative Zero Level}
\label{sec:relzero}

@@

\begin{deluxetable*}{llrrrrrrrrrr} 
\tabletypesize{\scriptsize}
\tablecolumns{11} 
\tablewidth{0pc} 
\tablecaption{\label{tab:global} Global Model Parameters} 
\tablehead{
\colhead{Number} &
\colhead{Model} &
\colhead{$f_1$} &
\colhead{$q_1/q_2$} & 
\colhead{$\beta_1$} & 
\colhead{$\beta_2$} &
\colhead{$T_2$} &
\colhead{$T_1$} &
\colhead{$n$} &
\colhead{D.O.F.} &
\colhead{$\chi^2$} &
\colhead{$\chi^2_{\nu}$}
}
\startdata
 1 & FDS99 best-fit  & 0.0363 & 13.0  & 1.67 & 2.70 & 15.72 &  9.15 & 1.018 & 7 & 23.9 & 3.41 \\
 2 & FDS99 general   & 0.0485 & 8.22  & 1.63 & 2.82 & 15.70 &  9.75 & 0.980 & 3 & 3.99 & 1.33 \\
 3 & single MBB      &  1.0   &  ...  & 1.59 &  ... &  ...  & 19.63 & 0.999 & 6 & 33.9 & 5.65 \\ [-2ex]
\enddata
\end{deluxetable*}

@@

FDS99 determined the best-fit values of the two-component model global 
parameters $\beta_1$, $\beta_2$, $q_1/q_2$ and $f_1$ via a correlation slope
analysis incorporating DIRBE and FIRAS data. In this section, we seek to 
perform a correlation slope determination of these same global parameters, but
swapping the \PLANCK~HFI maps for FIRAS at low frequencies, while still 
relying on DIRBE at higher frequencies. We also seek to determine via this
correlation slope analysis whether or not the combination of \PLANCK+DIRBE data
favors two-component models over single-MBB models in the same way that the
FIRAS+DIRBE data did in the FDS99 analysis.

In the two-component model case, we wish to obtain estimates for six 
free parameters: $\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall 
spectrum normalization $n$. The constraints employ are the correlation
slopes of each of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz),
140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz) against \PLANCK~857 GHz. We will 
refer to the slope for band $\nu_i$ as $s_{i,857}$. All of the correlations are
performed using $1^{\circ}$ smoothed maps. The slopes for \PLANCK~100-545 GHz 
are taken to be those from the relative zero level fits of 
\ref{sec:relzero}, and are illustrated by the dashed red lines in plots of 
Figure \ref{fig:dip}, right column. The 857 GHz slope is taken to be unity by 
definition. We use the SFD98 reprocessings of the DIRBE bands. Including 857 
GHz, we thus have 9 correlation slope constraints for six free parameters. 
Including DIRBE 140$\mu$m and 240$\mu$m is critical in making this problem 
sufficiently constrained, and also in providing information near the peak of 
the dust SED at $\sim$140$\mu$m, which is particularly sensitive to the 
presence of a single versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

We assume an uncertainty of 2\% on each of the 9 correlation slopes and
minimize the $\chi^2$ given by:

% hmm it's really seeming like I need to move the color correction section
% to be before this, because I need the \tilde{I} things in this equation

\begin{equation}
\chi^2 = \sum_{i=0}^{8}\frac{(s_{i, 857}-n\tilde{I}_{\nu_i}/\tilde{I}_{857})^2}{\sigma_{s}^2}
\end{equation}

%In light of the \PLANCK~HFI data, it is possible to revisit the best-fit 
%global parameters of the two-component emission model. To derive the 
%\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
%maps, we employed a correlation slope analysis (see Figure XX). Specifically,
%we correlated the observed \PLANCK~data against the appropriate FDS99 
%prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
%consideration due to the sensitivity of the 100 GHz trend to our ad hoc
%low order corrections (see Figure \ref{fig:harm}). All comparisons between
%\PLANCK~and the FDS99 predictions were made after smoothing both to 
%$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
%pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
%excellent.

@@

%However, the slopes at low frequencies are not precisely unity, as would
%be expected if the global two-component parameters derived from FIRAS by
%FDS99 were also the best-fitting global parameters with respect to the 
%\PLANCK~data set.

@@

%We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
%the correlation slopes and their uncertainties given in Table QQ by 
%taking $T_2$=$16.2$K and running Markov chains to sample the posterior:

%Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
%strong covariances, but even so several conclusions are clear: (1) a lower 
%value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
%the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
%is effectively identical to that found by FDS99 to within uncertainties and 
%(3)
%a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
%\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
%strongly covariant with $\beta_1$, the difference of $f_1$ between the 
%\PLANCK~and FIRAS best fits is not particularly significant.

@@

%The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
%separately for both model 1 (FIRAS+\verb|i100|) and model 2 
%(\PLANCK+\verb|i100|), each defined by their respective global parameters 
%listed in Table \ref{tab:global}.
